\ldots

### 2016-02-16 paper.tex
Shortening the paper.

Vector space models of language were inspired by the idea of \newcite{harris1954distributional} and \newcite{firth1957lingtheory} that meanings of words can be deduced from their co-occurrence with other words in natural text. If a word co-occurs with a context word more often than can be expected, this context word is indicative of the word's meaning, while the opposite indicates disjointness in meaning.
\newcite{Dagan:1993:CWS:981574.981596} were among the first to apply this idea computationally and to represent word meaning by an ordered range of values of
\emph{mutual information}\footnote{Also known as pairwise or pointwise mutual information and commonly abbreviated as PMI.} \cite{church1990word}.
Each value expresses the ratio between the observed and the expected co-occurrence, and, therefore, measures the association of the target word with a reference word. A word could thus be expressed as a vector with a set of contextual terms as its features, and as their weights a measure of association. This idea forms the basis of distributional semantics and has become mainstream in information retrieval and natural language processing tasks.

Over the last decades, various information-theoretic alternatives and refinements to mutual information have been introduced to capture lexical semantics. The most notable are \emph{positive PMI} (PosPMI, \newcite{BullinariaLevy07}) and \emph{local mutual information} (LMI, \newcite{evert2008corpora}).
These measures differ from PMI in their treatment of frequencies below expectation, and in the weight assigned to observed frequencies, embodied in additional multiplication factors.

@@

Table~\ref{tab:parameters} lists the parameters and their values used in this work.

@@

Figure~\ref{fig:performance-mean-var} shows the mean performance and the variance of the models grouped by vector dimensionality and the frequency component on the SimLex-999 dataset.

PMI models have the highest score variance, which peaks for the 10K dimensional models, however \NPMI/'s score variance has a different pattern: it almost does not depend on the vector dimensionality.

CPMI models exhibit the low variance for the models with dimensionality less than 5K, but the average \NCPMI/ performance decreases as the dimensionality increases due to the increase in score variance.

Shifted PMI has the lowest variance with the 10K dimensional models. \logNSPMI/ variance stabilizes after 10K dimensions, but \SPMI/ variance increases similarly to \CPMI/.

Finally, SCPMI behaves very similarly to SPMI but with higher variance.

High variance suggests that there are particular parameter combinations that weaken or strengthen the results of the lowly and highly dimensional models.

\subsection{Parameter interaction and heuristic derivation}

>>>>

% Vector space models of language were inspired by the idea of \newcite{harris1954distributional} and \newcite{firth1957lingtheory} that meanings of words can be deduced from their co-occurrence with other words in natural text. If a word co-occurs with a context word more often than can be expected, this context word is indicative of the word's meaning, while the opposite indicates disjointness in meaning.
% \newcite{Dagan:1993:CWS:981574.981596} were among the first to apply this idea computationally and to represent word meaning by an ordered range of values of
% \emph{mutual information}\footnote{Also known as pairwise or pointwise mutual information and commonly abbreviated as PMI.} \cite{church1990word}.
% Each value expresses the ratio between the observed and the expected co-occurrence, and, therefore, measures the association of the target word with a reference word. A word could thus be expressed as a vector with a set of contextual terms as its features, and as their weights a measure of association. This idea forms the basis of distributional semantics and has become mainstream in information retrieval and natural language processing tasks.

% Over the last decades, various information-theoretic alternatives and refinements to mutual information have been introduced to capture lexical semantics. The most notable are \emph{positive PMI} (PosPMI, \newcite{BullinariaLevy07}) and \emph{local mutual information} (LMI, \newcite{evert2008corpora}).
% These measures differ from PMI in their treatment of frequencies below expectation, and in the weight assigned to observed frequencies, embodied in additional multiplication factors.

@@

@@

Table~\ref{tab:parameters} lists parameters used in this work, their values and the proportion of score variance explained by the parameter and it's two-way interaction corresponding to the reduction in adjusted $R^2$ (0.61 if all parameters and their combinations are taken into account) if this parameter is left out using the analysis of variance, where the model score is a dependant variable and the model parameters are independent variables, refer to \newcite{lapesa2014large} for more details.

% ----------

% Figure~\ref{fig:performance-mean-var} shows the mean performance and the variance of the models grouped by vector dimensionality and the frequency component on the SimLex-999 dataset.

% PMI models have the highest score variance, which peaks for the 10K dimensional models, however \NPMI/'s score variance has a different pattern: it almost does not depend on the vector dimensionality.

% CPMI models exhibit the low variance for the models with dimensionality less than 5K, but the average \NCPMI/ performance decreases as the dimensionality increases due to the increase in score variance.

% Shifted PMI has the lowest variance with the 10K dimensional models. \logNSPMI/ variance stabilizes after 10K dimensions, but \SPMI/ variance increases similarly to \CPMI/.

% Finally, SCPMI behaves very similarly to SPMI but with higher variance.

% High variance suggests that there are particular parameter combinations that weaken or strengthen the results of the lowly and highly dimensional models.

\subsection{Heuristic derivation}
